Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-10-25 ltx/first_order_framework/LaTeX_Manuscript.tex
added poster

For models to be clinically viable, they must be patient-specific. A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cowan (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models, or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, to patient-specific data. Fitting the neural models to individuals is a highly non-trivial task. Recently, however, this taks has been approached from a number of standpoints.

\dean{Need to add extra references between here}
An estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has been proposed for studying evoked potential dynamics. Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations~\cite{Jansen1995}. Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations~\cite{schiff2008kalman}. This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation on spatiotemporal neural fields. This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
\dean{and here}

>>>>

For models to be clinically viable, they must be patient-specific. A possible approach to achieve this would be to fit a general continuum neural field model, like the Wilson and Cowan (WC)~\cite{Wilson1973} or Amari~\cite{Amari1977} models, or a neural mass model like the Jansen and Ritt model~\cite{Jansen1995}, to patient-specific data. Fitting the neural models to individuals is a highly non-trivial task. Recently, however, this task has been approached from a number of standpoints.

\dean{Need to add extra references between here}

An estimation framework for neural mass models known as dynamical causal modelling (DCM) \cite{David2003,David2006} has been proposed for studying evoked potential dynamics. Via a Bayesian inference scheme, DCM estimates the long range (cortico-cortical) connectivity structure between the specific isolated brain regions that best explains a given data set using the Jansen and Ritt equations~\cite{Jansen1995}. Another recent approach estimates the parameters of a neural field model using an unscented Kalman filter based on modified WC neural field equations~\cite{schiff2008kalman}. This work takes a system theoretic approach to the neural estimation problem, successfully demonstrating that it is possible to perform state estimation on spatiotemporal neural fields. This marks the first step in what has the potential to revolutionise the treatment of many neurological diseases where therapeutic electrical stimulation is viable.
\dean{and here}
